Convex Surrogates via Polyhedral Losses

### 2019-01-31 cvx-fin.tex
Added some definitions

\subsection{Properties and Losses}
\begin{definition}
  Property $\Gamma:\simplex\toto\R$

  Level set $\Gamma_r$

@@

  Redundant, finite \raf{I think to avoid a TON of extra mentions of ``non-redundant'' we should take finite to mean finite and non-redundant}
\end{definition}

@@

  A loss $L:\R\to\reals^\Y_+$, elicits a property $\Gamma:\simplex \toto \R$ if, for all $p \in \simplex$ and $r \in \Gamma(p)$, we observe
  \begin{equation}
   = \argmin_r \E_{Y\sim p}[L(r,Y)]
  \end{equation}
  \jessie{Do we want regular elicitation vs essentially elicits...}
\end{definition}

>>>>

\subsection{Properties and Losses}
\begin{definition}
  A property $\Gamma:\simplex\toto\R$ is a nonempty, set-valued function mapping a probability distribution to the correct report values for the given distribution.

  A \emph{level set} $\Gamma_r := \{p : r \in \Gamma(p)\}$ is the set of distributions $p$ for which the report $r$ is ``optimal''.

@@

  \raf{I think to avoid a TON of extra mentions of ``non-redundant'' we should take finite to mean finite and non-redundant}
  We call $\Gamma$ a \emph{finite} property is $\R$ is finite, and \emph{nonredundant} if, for all $r$, there is no $u$ so that the level set $\Gamma_r \subseteq \Gamma_u$.
  For simplicity, when we say a property is finite, we also take it to be nonredundant.
\end{definition}

@@

  A loss $L:\R\to\reals^\Y_+$, elicits a property $\Gamma:\simplex \toto \R$ if, for all $p \in \simplex$ and $r \in \Gamma(p)$, we observe
  \begin{equation}
  \Gamma(p) = \argmin_{r \in \R} \E_{Y\sim p}[L(r,Y)]
  \end{equation}
  \jessie{Do we want regular elicitation vs essentially elicits...}
\end{definition}
